Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-18 ICML2019/main.tex
fix bugs in accuracy

%  Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.\\  
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.\\
Instantiating $t$ with specific values ($1, 2, 3$ for example), we get the following accuracy equations on Laplace mechanism:
\begin{align*}
&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}\\
&= 0.19673467014,\\
&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} }\\ 
&= 0.11932560927,\\
&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} \\
&= 0.07237464051.
\end{align*}
In all cases above, probability values are fixed even data size changes, only the distance are decreasing.

@@

Given $t$ with the same specific values ($1, 2, 3$ as above), we get the following accuracy equations on improved Laplace mechanism:
%Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$. 
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
\begin{align*}
&\ilapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}\\
&= 0.31606027941,\\
&\ilapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} }\\
&= 0.11627207896,\\
&\ilapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}\\
&= 0.04277410743.
\end{align*}
In all cases above, probability values are fixed even data size changes, only the distance are decreasing.

\subsection{Accuracy Bound for $\hexpmech$}
\label{subsec_accuracy_smoo}
  In Beta-binomial model,
  we have following formula for accuracy:
%  \begin{align*}
%  \label{eq_acc}
%  & \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  }\\ 
%  = & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}},
%  \end{align*}
%
%  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$
  \begin{align*}
  \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  } }\\ 
  &  = \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}\\
  & \text{ where } c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
  \end{align*}

>>>>

%  Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.\\  
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.\\
Instantiating $t$ with specific values ($0,1,2$ for example), we get the following accuracy equations on Laplace mechanism:
\begin{align*}
&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}\\
&= 0.19673467014,\\
&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} }\\ 
&= 0.11932560927,\\
&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} \\
&= 0.07237464051.
\end{align*}
In all cases above, probability values are fixed even data size changes, only the distance are decreasing.

@@

Given $t$ with the same specific values ($0,1,2$ as above), we get the following accuracy equations on improved Laplace mechanism:
%Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$. 
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
\begin{align*}
&\ilapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}\\
&= 0.31606027941,\\
&\ilapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} }\\
&= 0.11627207896,\\
&\ilapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}\\
&= 0.04277410743.
\end{align*}
In all cases above, probability values are fixed even data size changes, only the distance are decreasing.

\subsection{Accuracy Bound for $\hexpmech$}
\label{subsec_accuracy_smoo}
\begin{lem}
\label{lem_acc_hexp}
  In Beta-binomial model,
  we have following accuracy bound for this mechanism:
%  \begin{align*}
%  \label{eq_acc}
%  & \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  }\\ 
%  = & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}},
%  \end{align*}
%
%  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$

  \begin{align*}
  \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  } }\\ 
  &  = \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}\\
  & \text{ where } c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
  \end{align*}
\end{lem}
